Subject-specific curves for time series forecasting of smart meter demand

### 2019-11-03 sscts-paper-1.Rmd
Caching and smaller chunks

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  # dev = "pdf",
  dev = "png",
  dpi = 200,
  fig.height = 5 * 1.4,
  fig.width = 8 * 1.4
)

rm(list = ls())

library(tidyverse)
library(tsibble)
library(furrr)
library(lubridate)
library(stringr)
library(lme4)
# library(nlme)
library(splines)
library(forecast)
library(leaps)
source("R/load-data.R")
source("R/feature-selection.R")
source("R/test-models.R")
source("R/models-lme4.R")
source("R/plot-helpers.R")

# packages .bib file
knitr::write_bib(c("base", "lme4"),
  "packages.bib",
  width = 60
)

@@

# The base::scale function returns a matrix which causes issues later on when
# fitting and predicting with lm. Use this because it returns a vector.
scale_dbl <- function(x) {
  (x - mean(x)) / sd(x)
}

#### Parameters ===============================================================
# Data
data_dir <- "/mnt/Documents/data/building_level"
qh_path <- file.path(data_dir, "qh_2018")
outlier_file <- file.path(data_dir, "outlier_dates_20181120.csv")
attribute_file <- file.path(data_dir, "attributes_20181019_tidy.csv")
building_list_file <- file.path(data_dir, "building_list_20181022.csv")
all_data_file <- "cache/main_df.RData"
fs_df_file <- "cache/fs_df.RData"
model_df_file <- "cache/model_df.RData"

@@

# Presentation
p_one_day_ahead_date <- dmy("23/8/2017")
scenario_bid <- "BID0010"
scenario_dates <- ymd("2017-01-09") + 0:4
business_hour_periods <- 29:76

#### Setup ====================================================================
# Run if qh .RData file hasn't been created
if (!file.exists(all_data_file)) {
  cat("Processing data...\n\n")
  main_df <- load_all_data(
    attribute_file = attribute_file,
    qh_path = qh_path,
    building_list_file = building_list_file,
    business_days = TRUE
  )

@@

# Calculate other variables
n_buildings <- length(unique(main_df$bid))
fcst_test_dates <- as_date(intersect(fcst_test_dates, unique(main_df$date)))

#### Feature selection ========================================================
if (!file.exists(fs_df_file)) {
  cat(
    "Running feature selection for max of", n_max_features,
    "candidate predictors...\n\n"
  )
  start_time <- Sys.time()
  fs_df <- list(
    month = unique(month(fcst_test_dates)),
    period = fcst_test_periods
  ) %>%
    cross_df() %>%
    mutate(fs_date = map(
      month,
      ~ min(fcst_test_dates[month(fcst_test_dates) == .x])
    )) %>%
    unnest() %>%
    mutate(features = future_map2(
      fs_date,
      period,
      select_features,
      train_window = fcst_train_window,
      min_train_days = fcst_min_train_days,
      n_var_max = n_max_features,
      .progress = TRUE
    ))

@@

fs_df <- fs_df %>%
  mutate(vars = map(features, ~ .x %>%
    # filter(bic == min(bic)) %>%
    filter(loocv == min(loocv)) %>%
    pull(vars) %>%
    unlist()))

#### Fit models ===============================================================
if (!file.exists(model_df_file)) {
  cat("Fitting models...\n\n")
  start_time <- Sys.time()

>>>>

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.lazy = FALSE,
  # dev = "pdf",
  dev = "png",
  dpi = 200,
  fig.height = 5 * 1.4,
  fig.width = 8 * 1.4
)
library(tidyverse)
library(tsibble)
library(furrr)
library(lubridate)
library(stringr)
library(lme4)
# library(nlme)
library(splines)
library(forecast)
library(leaps)
source("R/load-data.R")
source("R/feature-selection.R")
source("R/test-models.R")
source("R/models-lme4.R")
source("R/plot-helpers.R")
```

```{r init}
# packages .bib file
knitr::write_bib(c("base", "lme4"),
  "packages.bib",
  width = 60
)

@@

# The base::scale function returns a matrix which causes issues later on when
# fitting and predicting with lm. Use this because it returns a vector.
scale_dbl <- function(x) {
  (x - mean(x)) / sd(x)
}
```

```{r parameters}
#### Parameters ===============================================================
# Data
data_dir <- "/mnt/Documents/data/building_level"
qh_path <- file.path(data_dir, "qh_2018")
outlier_file <- file.path(data_dir, "outlier_dates_20181120.csv")
attribute_file <- file.path(data_dir, "attributes_20181019_tidy.csv")
building_list_file <- file.path(data_dir, "building_list_20181022.csv")
all_data_file <- "cache/main_df.RData"
fs_df_file <- "cache/fs_df.RData"
model_df_file <- "cache/model_df.RData"

@@

# Presentation
p_one_day_ahead_date <- dmy("23/8/2017")
scenario_bid <- "BID0010"
scenario_dates <- ymd("2017-01-09") + 0:4
business_hour_periods <- 29:76
```

```{r main}
#### Setup ====================================================================
# Run if qh .RData file hasn't been created
if (!file.exists(all_data_file)) {
  cat("Processing data...\n\n")
  main_df <- load_all_data(
    attribute_file = attribute_file,
    qh_path = qh_path,
    building_list_file = building_list_file,
    business_days = TRUE
  )

@@

# Calculate other variables
n_buildings <- length(unique(main_df$bid))
fcst_test_dates <- as_date(intersect(fcst_test_dates, unique(main_df$date)))
```

```{r features}
#### Feature selection ========================================================
if (!file.exists(fs_df_file)) {
  cat(
    "Running feature selection for max of", n_max_features,
    "candidate predictors...\n\n"
  )
  start_time <- Sys.time()
  fs_df <- list(
    month = unique(month(fcst_test_dates)),
    period = fcst_test_periods
  ) %>%
    cross_df() %>%
    mutate(fs_date = map(
      month,
      ~ min(fcst_test_dates[month(fcst_test_dates) == .x])
    )) %>%
    unnest() %>%
    mutate(features = future_map2(
      fs_date,
      period,
      select_features,
      train_window = fcst_train_window,
      min_train_days = fcst_min_train_days,
      n_var_max = n_max_features,
      .progress = TRUE
    ))

@@

fs_df <- fs_df %>%
  mutate(vars = map(features, ~ .x %>%
    # filter(bic == min(bic)) %>%
    filter(loocv == min(loocv)) %>%
    pull(vars) %>%
    unlist()))
```

```{r models}
#### Fit models ===============================================================
if (!file.exists(model_df_file)) {
  cat("Fitting models...\n\n")
  start_time <- Sys.time()
